`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-24 inst/manuscript/manuscript.rmd
Add an draft abstract;

#Abstract

##Contact
jog2030@qatar-med.cornell.edu

>>>>

#Abstract
Dithionite scramblase assays are an established means of probing the lipid 
scrambling activity of protein extracts and purified proteins. While the assay
has yielded insight into the scramblase activity in crude membrane preparations,
functional validation of candidate scramblases, stoichiometry of scramblase 
complexes and probe ATP-dependence of flippases, data analysis in its context 
has remained a task involving many manual steps. With the extension package 
`flippant` to `R`, a free software environment for statistical computing and 
graphics, we introduce an integrated solution for the analysis and 
publication-grade graphical presentation of dithionite scramblase assays and 
demonstrate its utility in a reanalysis of manual analysis from the publication
record, closely reproducing the reported results.
